Finding Quality Issues in SKOS Vocabularies

### 2012-03-27 analysis.tex
fixed table caption error
alphabetic ordering of table 2

\begin{table}[h]
\caption{Results of the quality checking functions \todo{CM}{order alpha}}
\label{tab:results}

@@

\begin{tabular}{lccccccccccccccc}
\textbf{Issue} & \rotatebox{90}{\textbf{GTAA}} & \rotatebox{90}{\textbf{Geonames}} & \rotatebox{90}{\textbf{MeSH}} & \rotatebox{90}{\textbf{PXV}} & \rotatebox{90}{\textbf{Eurovoc}} & \rotatebox{90}{\textbf{IPSV}} & \rotatebox{90}{\textbf{Agrovoc}} & \rotatebox{90}{\textbf{DBpedia}} & \rotatebox{90}{\textbf{Pressinfo}} & \rotatebox{90}{\textbf{NYTP}} & \rotatebox{90}{\textbf{LCSH}} & \rotatebox{90}{\textbf{Meketre}} & \rotatebox{90}{\textbf{STW}} & \rotatebox{90}{\textbf{NAICS}} & \rotatebox{90}{\textbf{LVAk}} \\
\toprule
Omitted or Invalid Language Tags & 0 & 0 & 23,950 & 1,578 & n/a & 0 & 0 & 0 & 1,224 & 0 & 18 & 0 & 2 & n/a & 13,411 \\

Incomplete Language Coverage & 0 & 0 & 0 & 0 & n/a & 0 & 32,035 & 0 & 0 & 0 & 0 & 420 & 6,456 & n/a & 0 \\

Undocumented Concepts & 96,850 & 0 & 1,807 & 1,918 & 5,341 & 4,551 & 32,035 & 743,410 & 1,125 & 4,094 & 398,036 & 422 & 5,236 & 3,259 & 13,411 \\

Label Conflicts & 12,404 & 18 & 0 & 7 & n/a & 0 & 2,949 & 0 & 0 & 0 & n/a & 4 & 5 & n/a & 13 \\

@@

Orphan Concepts & 162,000 & 671 & 0 & 2 & 7 & 0 & 0 & 77,062 & 1,125 & 4,979 & 172,364 & 0 & 4 & 0 & 21 \\

Weakly Connected Components & 621 & 0 & 4 & 10 & 4 & 1 & 4 & 1,506 & 0 & 0 & 22,131 & 5 & 1 & 1 & 11 \\

Cyclic Hierarchical Relations & 0 & 0 & 4 & 0 & 0 & 0 & 0 & 1,132 & 0 & 0 & 0 & 0 & 0 & 0 & 5 \\

Valueless Associative Relations & 9,438 & 0 & 495 & 0 & 1 & 239 & 282 & 8,120 & 0 & 0 & 1,879 & 0 & 5,082 & 0 & 5 \\

Solely Transitively Related Concepts & 0 & 0 & 0 & 0 & 2,652 & 0 & 0 & 0 & 0 & 0 & 0 & 36 & 0 & 2,189 & 0 \\

Omitted Top Concepts & 9 & 9 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 1 & 19 & 0 & 0 & 0 & 0 \\

Top Concept Having Broader Concepts & 0 & 0 & 0 & 1 & 0 &0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\

@@

Missing In-Links & 171,980* & 19 & 24625 & 1,686 & 6,796 & 3,080 & 32,035 & 733,800* & 1,125 & 20 & 404,540* & 422 & 6,516 & 2,213 & 13,411 \\

Missing Out-Links & 171,991 & 671 & 24626 & 1,472 & 6,797 & 0 & 32,035 & 743,410 & 1,116 & 0 & 408,198 & 273 & 6,524 & 0 & 13,411 \\

Broken Links & 0 & 0 & 1 & 163 & 0* & 1 & 238 & 0* & 11 & 7 && 425 & 1 & 3,169 & n/a \\

Undefined SKOS Resources & 0 & 0 & 1 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0  \\

>>>>

\begin{table}[h]
\caption{Results of the quality checking functions}
\label{tab:results}

@@

\begin{tabular}{lccccccccccccccc}
\textbf{Issue} & \rotatebox{90}{\textbf{AGROVOC}} & \rotatebox{90}{\textbf{DBpedia}} & \rotatebox{90}{\textbf{Eurovoc}} & \rotatebox{90}{\textbf{Geonames}} & \rotatebox{90}{\textbf{GTAA}} & \rotatebox{90}{\textbf{IPSV}} & \rotatebox{90}{\textbf{LCSH}} & \rotatebox{90}{\textbf{LVAk}} & \rotatebox{90}{\textbf{Meketre}} & \rotatebox{90}{\textbf{MeSH}} & \rotatebox{90}{\textbf{NAICS}} & \rotatebox{90}{\textbf{NYTP}} & \rotatebox{90}{\textbf{Pressinfo}} & \rotatebox{90}{\textbf{PXV}} & \rotatebox{90}{\textbf{STW}} \\

\toprule
Omitted or Invalid Language Tags & 0 & 0 & n/a & 0 & 0 & 0 & 18 & 13,411 & 0 & 23,950 & n/a & 0 & 1,224 & 1,578 & 2 \\

Incomplete Language Coverage & 32,035 & 0 & n/a & 0 & 0 & 0 & 0 & 0 & 420 & 0 & n/a & 0 & 0 & 0 & 6,456 \\

Undocumented Concepts & 32,035 & 743,410 & 5,341 & 0 & 96,850 & 4,551 & 398,036 & 13,411 & 422 & 1,807 & 3,259 & 4,094 & 1,125 & 1,918 & 5,236 \\

Label Conflicts & 2,949 & 0 & n/a & 18 & 12,404 & 0 & n/a & 13 & 4 & 0 & n/a & 0 & 0 & 7 & 5 \\

@@

Orphan Concepts & 0 & 77,062 & 7 & 671 & 162,000 & 0 & 172,364 & 21 & 0 & 0 & 0 & 4,979 & 1,125 & 2 & 4 \\

Weakly Connected Components & 4 & 1,506 & 4 & 0 & 621 & 1 & 22,131 & 11 & 5 & 4 & 1 & 0 & 0 & 10 & 1 \\

Cyclic Hierarchical Relations & 0 & 1,132 & 0 & 0 & 0 & 0 & 0 & 5 & 0 & 4 & 0 & 0 & 0 & 0 & 0 \\

Valueless Associative Relations & 282 & 8,120 & 1 & 0 & 9,438 & 239 & 1,879 & 5 & 0 & 495 & 0 & 0 & 0 & 0 & 5,082 \\

Solely Transitively Related Concepts & 0 & 0 & 2,652 & 0 & 0 & 0 & 0 & 0 & 36 & 0 & 2,189 & 0 & 0 & 0 & 0 \\

Omitted Top Concepts & 0 & 0 & 1 & 9 & 9 & 0 & 19 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\

Top Concept Having Broader Concepts & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 \\

@@

Missing In-Links & 32,035 & 733,800 & 6,796 & 19 & 171,980* & 3,080 & 404,540* & 13,411 & 422 & 24,625 & 2,213 & 20 & 1,125 & 1,686 & 6,516 \\

Missing Out-Links & 32,035 & 743,410 & 6,797 & 671 & 171,991 & 0 & 408,198 & 13,411 & 273 & 24,625 & 0 & 0 & 1,116 & 1,472 & 6,524 \\

Broken Links & 238 & 0* & 0* & 0 & 0 & 1 && n/a & 425 & 1 & 3,169 & 7 & 11 & 163 & 1 \\

Undefined SKOS Resources & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
